A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Make refs to tech report
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1059 43ef1190-90fd-4dd7-a769-d0121f02b80e

\documentclass{llncs}
%\documentclass{sig-alternate}
\usepackage[english,british]{babel}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{appendix}

@@

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients may use these values to retrieve
the updated response only if the resource has changed. Other relevant
headers are described in Table~\ref{tab:headers}
in Appendix~\ref{app:fetcher}.\todo{ref report}\todo{More on HTTP}

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN, which is also used to manage the datasets
in the ``LOD cloud'')\todo{expand on the coverage}, as well as other sources. To compile a list of
candidates to further examine, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process is given in Appendix~\ref{app:reduction}.\todo{more
  detail on filtering}

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL endpoints, vocabularies, or other information
resources, by a spider detailed in Appendix~\ref{app:fetcher},
resulting in 7745 requests, done on 2015-01-02. Although this is not a
very large number, we assume that caching headers are usually set on a
per-host basis, if any differences exist, they are likely on different
types, and so the number of hosts is more important than the
number of resources.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in Appendix~\ref{app:stats}, we find in
both the cases of standards-compliant freshness lifetime and for the other
usable metadata, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints.\todo{elaborate}

@@

As shown in Table~\ref{tab:headers}, there are also other caching
headers than those mentioned in the introduction. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.

@@

In this work, we have only explored the cases where the server is
cooperative, in the sense that message data or metadata provides at
least a hint of a resource's cacheability. We also noted that the
majority of the Semantic Web is unhelpful. Therefore, an interesting
direction is to learn the change frequency of resources to use in a
heuristic freshness lifetime estimation. However, such work should
operate within the loose constraints of Section~4.2.2 in RFC7234, and
should find its niche when the other techniques described in this paper
are unavailable. Once this is done, the correctness of caching headers
should be assessed, possibly using contingency tables similar to those
in Appendix~\ref{app:stats}.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs}

>>>>

\documentclass{llncs}
%\documentclass{sig-alternate}
\usepackage[english,british]{babel}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{hyperref}

@@

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients may use these values to retrieve
the updated response only if the resource has changed. Other relevant
headers are described in a companion technical report
\cite{kjernsmo_add_survey_2015}.
% Table~\ref{tab:headers} in Appendix~\ref{app:fetcher}.
\todo{More on HTTP}

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN, which is also used to manage the datasets
in the ``LOD cloud'')\todo{expand on the coverage}, as well as other sources. To compile a list of
candidates to further examine, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process is given in the companion technical report
\cite{kjernsmo_add_survey_2015}.% Appendix~\ref{app:reduction}.
\todo{more detail on filtering}

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL endpoints, vocabularies, or other information
resources, by a spider detailed in the companion technical report
\cite{kjernsmo_add_survey_2015}, resulting in 7745 requests, done on
2015-01-02. Although this is not a very large number, we assume that
caching headers are usually set on a per-host basis, if any
differences exist, they are likely on different types, and so the
number of hosts is more important than the number of resources.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in the companion technical report
\cite{kjernsmo_add_survey_2015}, we find in
both the cases of standards-compliant freshness lifetime and for the other
usable metadata, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints.\todo{elaborate}

@@

The companion technical report \cite{kjernsmo_add_survey_2015}, lists other caching
headers than those mentioned in the introduction. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.

@@

In this work, we have only explored the cases where the server is
cooperative, in the sense that message data or metadata provides at
least a hint of a resource's cacheability. We also noted that the
majority of the Semantic Web is unhelpful. Therefore, an interesting
direction is to learn the change frequency of resources to use in a
heuristic freshness lifetime estimation. However, such work should
operate within the loose constraints of Section~4.2.2 in RFC7234, and
should find its niche when the other techniques described in this paper
are unavailable. Once this is done, the correctness of caching headers
should be assessed, possibly using contingency tables similar to those
in the companion technical report \cite{kjernsmo_add_survey_2015}.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{egne,webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs,similarity,optimization}
